### 2020-04-21 survival.tex
spell

Very few failures have occurred in the new batch and they are clarly
less prone to failure at the 2.5 year mark. There is a slight change
at the 3 year mark of cages 1 and 2 but it is also accompanied with a
rise in uncertainty and survival is still well above levels in the old
batch.

@@

We find that the average hazard ratios strongly correlate with
detailed nuances of the system cooling architecture.  The figures give
hazard ratios for each of the location variables, giving the ratio for
each level compared to its first (0) level (consequently the 0 level
is always 1). Due to the exponential nature of the CPH model, the
horizontal hazard ratio axis is on a log scale. The estimates include
uncertainty, which too is most reliably computed on a log scale (see,
for example, \cite{Ostrouchov88}). In the figures, we also include the
number of units, N, at risk and the number of events that occurred in
each category. All the factors ({\em col, row, cage, slot, node}) are
balanced with respect to the nunber of units at risk and consequently
nearly orthogonal (each level of a factor contains all levels of the
other factors) providing an almost ``designed'' experiment nature to
this analysis.

Our interpretation of correlation with detailed nuances of the cooling
system comes mostly from the hazard ratios for the old batch. The new
batch has mot had many failure events and the uncertainty bars of
nearly all ratios include 1, which is no difference. In the old batch,
we see that {\em cage} has the strongest effect, putting the highest
hazard ratio on cage 2, which is consistent with lowest survivals in
the KM analysis earlier. Its ratio value near 20 has to be interpreted
with caution because it is a time averaged value on a log scale. This
aspect is not captured by the uncertainty, which accounts for the
randomnes of the failures and not for the geometric time averaging
\cite{coxhazardinterpret}.

>>>>

Very few failures have occurred in the new batch and they are clearly
less prone to failure at the 2.5 year mark. There is a slight change
at the 3 year mark of cages 1 and 2 but it is also accompanied with a
rise in uncertainty and survival is still well above levels in the old
batch.

@@

We find that the average hazard ratios strongly correlate with
detailed nuances of the system cooling architecture.  The figures give
hazard ratios for each of the location variables, giving the ratio for
each level compared to its first (0) level (consequently the 0 level
is always 1). Due to the exponential nature of the CPH model, the
horizontal hazard ratio axis is on a log scale. The estimates include
uncertainty, which too is most reliably computed on a log scale (see,
for example, \cite{Ostrouchov88}). In the figures, we also include the
number of units, N, at risk and the number of events that occurred in
each category. All the factors ({\em col, row, cage, slot, node}) are
balanced with respect to the number of units at risk and consequently
nearly orthogonal (each level of a factor contains all levels of the
other factors) providing an almost ``designed'' experiment nature to
this analysis.

Our interpretation of correlation with detailed nuances of the cooling
system comes mostly from the hazard ratios for the old batch. The new
batch has mot had many failure events and the uncertainty bars of
nearly all ratios include 1, which is no difference. In the old batch,
we see that {\em cage} has the strongest effect, putting the highest
hazard ratio on cage 2, which is consistent with lowest survivals in
the KM analysis earlier. Its ratio value near 20 has to be interpreted
with caution because it is a time averaged value on a log scale. This
aspect is not captured by the uncertainty, which accounts for the
randomness of the failures and not for the geometric time averaging
\cite{coxhazardinterpret}.
